### 2018-03-19 two_terminal/paper.tex
added circuit diagram

\input{header}

\physics
\begin{document}
\papertitle{Two-Terminal Devices}
\paperauth{A}{Khesin}{1002442029}
\paperauth{P}{Zavyalova}{1002345036}
\paperdate{March 19, 2018, Completed March 13, 2018}
\begin{paperabs}

@@

>>>>

\input{header}
\physics
\begin{document}
\papertitle{Two-Terminal Devices}
\paperauth{A}{Khesin}{1002442029}
\paperauth{P}{Zavyalova}{1002345036}
\paperdate{March 19, 2018, Completed March 13, 2018}
\begin{paperabs}

@@

\paperfig{Circuit}{\begin{center}
\begin{tikzpicture}
\draw
(2,2) rectangle (3,3)
(2.5,2) |- (5,1.5)
(2.5,1.5) to[resistor] (2.5,0)
(1,0) -- (5,0)
(2.5,3) |- (5,3.5)
(2.5,3.5) to[resistor] (1,3.5) -- (1,2.1)
(-0.05,2.1) node[transformer core]{}
(4,0) node[ground]{}
(5,0) node[above]{\small Ground}
(5,1.5) node[above]{\small Y Input}
(5,3.5) node[below]{\small X Input}
(2.5,2.5) node[]{\small Device}
(2.7,0.9) node[right]{\small $R_2$}
(2.7,0.6) node[right]{\small\SI{4.7}{\ohm}}
(1.75,3.4) node[below]{\small $R_1$}
(0.5,1.3) node[right]{\small \SI{6.3}{\volt}}
(0.5,1) node[right]{\small RMS}
(0.5,0.7) node[right]{\small A. C.}
(-0.5,0.85) node[left]{\small A. C.}
(-0.5,1.15) node[left]{\small \SI{60}{\hertz}}
;
\end{tikzpicture}\end{center}}
{The circuit used in the experiment.
The value of $R_1$ was varied depending on what was used for the Device.
The $X$ and $Y$ nodes were connected to an oscilloscope.}
